### 2014-02-02 src/paper.Rnw
update

hist(log(10,m$pit.mutation.total), breaks=50, col=rgb(0,0,1,1/4), main='histogram of log(total) mutation score')
hist(log(10,m$pit.mutation.num), breaks=50, add=T, col=rgb(1,0,0,1/4))
@
\caption{Plots}
\label{fig:caddrm}
\end{figure*}

@@

$ \mu_\{M_{all} | M_{sdl}, M_{rnd}\} = 0 + \beta_1 {sdl} + \beta_2 M_{rnd} + \beta_3 M_{sdl} M_{rnd}  $
\begin{small}
<<results='asis'>>=
s <- subset(m, select=c(mut.avg,sdl.mut.avg))
s$type <- 'sdl'
colnames(s) <- c('mut', 'sample', 'type')
r <- subset(m, select=c(mut.avg,lrnd.mut.avg))
r$type <- 'rnd'
colnames(r) <- c('mut', 'sample', 'type')
all <- rbind(s, r)
detach(m)
fm <- with(all, lm(mut ~ sample + type + sample:type))
sm <- anova(fm)
print(xtable(sm,caption="My caption"), size="\\small")
@
\end{small}

@@

>>>>

hist(log(10,m$pit.mutation.total), breaks=50, col=rgb(0,0,1,1/4), main='histogram of log(total) mutation score')
hist(log(10,m$pit.mutation.num), breaks=50, add=T, col=rgb(1,0,0,1/4))
@
\caption{Plots of total mutation number, and those killed.}
\label{fig:caddrm}
\end{figure*}

@@

$ \mu_\{M_{all} | M_{sdl}, M_{rnd}\} = 0 + \beta_1 {sdl} + \beta_2 M_{rnd} + \beta_3 M_{sdl} M_{rnd}  $
\begin{small}
<<results='asis'>>=
s <- subset(m, select=c(mut.avg,sdl.mut.avg))
s$type <- 'sdl'
colnames(s) <- c('mut', 'sample', 'type')
r <- subset(m, select=c(mut.avg,lrnd.mut.avg))
r$type <- 'rnd'
colnames(r) <- c('mut', 'sample', 'type')
all <- rbind(s, r)
fm <- with(all, lm(mut ~ sample + type + sample:type))
sm <- anova(fm)
print(xtable(sm,caption="My caption"), size="\\small")
@
\end{small}

@@

\begin{figure*}[t]
<<tplots, fig.width=5, fig.height=5, out.width='.45\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
t_f <- sdl.time~lrnd.time
plot(t_f, main='SDL ~ RND',pch='*')
abline(lm(t_f), col='red')
detach(m)
@
\caption{Time}
\label{fig:caddrm}
\end{figure*}
